In the Crucible: Massive Compact Galaxies with High-Velocity Outflows and Eddington-Limited Star Formation

### 2012-04-17 tex/sigmasfr/ms.tex
more edits to section 2.2

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mgii}{\textrm{Mg}~\textsc{ii}}
\newcommand{\nev}{[\textrm{Ne}~\textsc{v}]}
\newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
\newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\mstar}{M$_{*}$}
\newcommand{\units}{M$_{\odot}$~yr$^{-1}$~kpc$^{-2}$}
\newcommand{\lrest}{\lambda_{\textnormal{\scriptsize{rest}}}}
\newcommand{\lobs}{\lambda_{\textnormal{\scriptsize{obs}}}}
\newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

@@

We gathered photometry from the All-Sky Release of the Wide-field
Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
General Release 6 from the Galaxy Evolution Explorer (GALEX).  We also
obtained $5\times30$~sec dithered exposures in the 3.6~$\mu$m and
4.5~$\mu$m for all sources with the Infrared Array Camera
\citep{faz04} on the Spitzer Space Telescope \citep{wer04} as part of
General Observer program 60145 (PI: C. Tremonti).  We used the
post--basic calibrated data to perform aperture photometry on all
sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  All the photometry was corrected for Galactic extinction
based on the \citet{sch98} dust maps.  We show spectral energy
distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12~$\mu$m detections by fitting \citet{cha01} templates to their
12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, the method of \citet{ruj12} yields SFRs that agree with
the above values within 0.05~dex.  We note that the shape of the IR
SED for star-forming galaxies depends on the surface density of star
formation \citep[e.g.,][]{ruj11,elb11}, with more compact starbursts
having larger total-IR (8--1000~$\mu$m) to mid-IR (8--24~$\mu$m)
ratios.  The extreme $\sigmasfr$ values of our sample imply large
total-IR to mid-IR ratios, characteristic of the most luminous
galaxies in the local universe \citep[e.g.,][]{cha01,dal02,rie09}.
For the 8/29 sources where we estimate $SFR_{IR}>200$~\msun~yr$^{-1}$
above, using the most luminous local templates would yield SFRs that
are larger by 0.5~dex.

We also estimate star-formation rates and stellar masses based on
stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
method of \citet{mou11}.  For galaxies with
$SFR_{IR}>50$~\msun~yr$^{-1}$, there is agreement between these
UV-optical-based estimates and $SFR_{IR}$ with a scatter of 0.32~dex.

@@

>>>>

\newcommand{\kms}{km~s$^{-1}$}
\newcommand{\mgii}{\textrm{Mg}~\textsc{ii}}
\newcommand{\nev}{[\textrm{Ne}~\textsc{v}]}
\newcommand{\oii}{[\textrm{O}~\textsc{ii}]}
\newcommand{\oiii}{[\textrm{O}~\textsc{iii}]}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\mstar}{M$_{*}$}
\newcommand{\units}{M$_{\odot}$~yr$^{-1}$~kpc$^{-2}$}
\newcommand{\lrest}{\lambda_{\textnormal{\scriptsize{rest}}}}
\newcommand{\lobs}{\lambda_{\textnormal{\scriptsize{obs}}}}
\newcommand{\sigmasfr}{\Sigma_{\textnormal{\scriptsize{SFR}}}}
\newcommand{\sfrir}{\textnormal{SFR}_{\textnormal{\scriptsize{IR}}}}
\newcommand {\apgt} {\ {\raise-.5ex\hbox{$\buildrel>\over\sim$}}\ }
\newcommand {\aplt} {\ {\raise-.5ex\hbox{$\buildrel<\over\sim$}}\ }

@@

We gathered photometry from the All-Sky Release of the Wide-field
Infrared Survey Explorer \citep[WISE,][]{wri10}, the Seventh Data
Release of the Sloan Digital Sky Survey \citep[SDSS,][]{aba09}, and
General Release 6 from the Galaxy Evolution Explorer
\citep[GALEX,][]{mar05galex}.  We also obtained $5\times30$~sec
dithered exposures at 3.6~$\mu$m and 4.5~$\mu$m for all sources with
the Infrared Array Camera \citep{faz04} on the Spitzer Space Telescope
\citep{wer04} as part of General Observer program 60145 (PI:
C. Tremonti).  We used the post--basic calibrated data to perform
aperture photometry on all sources, and we also used the
APEX\footnote{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/tools/mopex/}
point-source extraction software for photometry of sources in crowded
fields.  All the photometry was corrected for Galactic extinction
based on the \citet{sch98} dust maps.  We show spectral energy
distributions (SEDs) for the three high-$\sigmasfr$ galaxies in
Figure~\ref{fig:seds}.

We estimate IR-based star-formation rates for the 25/29 galaxies with
WISE 12 or 22~$\mu$m detections by fitting \citet{cha01} templates to
their 12 and 22~$\mu$m fluxes.  For the 14/29 galaxies with 22~$\mu$m
detections, this yields SFRs that agree with those obtained from the
\citet{ruj12} method based on 24~$\mu$m luminosity (with a scatter of
0.05~dex).  We note that several authors have shown that the shape of
the IR SED for star-forming galaxies depends on the surface density of
star formation \citep[e.g.,][]{ruj11,elb11}, with more compact
starbursts having larger total-IR (8--1000~$\mu$m) to mid-IR
(8--24~$\mu$m) ratios.  The extreme $\sigmasfr$ values of our sample
imply large total-IR to mid-IR ratios, characteristic of the most
luminous galaxies in the local universe
\citep[e.g.,][]{cha01,dal02,rie09}.  For the 8/29 sources with SFRs in
the ULIRG regime ($\sfrir>200$~\msun~yr$^{-1}$), we would obtain SFRs
that are larger by 0.5~dex (compared to the values obtained above) if
we used the most luminous local templates.

We also estimate star-formation rates and stellar masses based on
stellar population fits to the $\lrest=0.1$--3~$\mu$m SEDs using the
method of \citet{mou11}.  For galaxies with
$\sfrir>50$~\msun~yr$^{-1}$, there is agreement between these UV-based
SFR estimates and $\sfrir$ with a scatter of 0.32~dex.  We find a
median extinction of $A_V=0.4$~mag for an SMC-based dust law.

@@

\bibitem[Martin et al.(2005)]{mar05galex} Martin, D.~C., Fanson, J.,
  Schiminovich, D., et al.\ 2005, \apjl, 619, L1
